Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-08-01 sections/abstract.tex
reword

\begin{abstract}
Modern Code Review (MCR) where reviewers virtually discuss proposed changes by adding comments through a code review tool or a mailing list has  received much attention recently due to its perceived cost-effectiveness and popularity with industrial and OSS projects. Recent studies have indicated a positive relationship between the number of review comments and code quality. However little research exists investigating how such discussion impacts software quality. In fact there has been concern that the informality of MCR encourages a focus on trivial, tangential, or unrelated  issues. Indeed we have observed that such comments are quite frequent and may even constitute the majority.  We conjecture that an effective MCR actually depends on having a substantive quantity of comments that directly impact a proposed change (or are "useful"). To investigate this, a necessary step requires distinguishing review comments that are useful to a proposed change from those that are not. For a large OSS project such as our Qt case study, manual assessment of the over 72,000 comments is a daunting task.  We propose that semantic similarity is a practical, cost-efficient, and empirically assurable approach for assisting with such assessments. Our case-study results indicate that our approach can classify comments with significant precision and recall and reduce classification effort by about 77\%.

>>>>

\begin{abstract}
Modern Code Review (MCR)---where reviewers virtually discuss proposed changes by adding comments through a code review tool or a mailing list---has received much attention recently due to its perceived cost-effectiveness and popularity with industrial and OSS projects.
Recent studies have indicated a positive relationship between the number of review comments and code quality.
However, little research exists investigating how such discussion impacts software quality.
In fact, there has been concern that the informality of MCR encourages a focus on trivial, tangential, or unrelated issues.
Indeed, we have observed that such comments are quite frequent and may even constitute the majority.
We conjecture that an effective MCR actually depends on having a substantive quantity of comments that directly impact a proposed change (or are ``useful'').
To investigate this, a necessary step requires distinguishing review comments that are useful to a proposed change from those that are not.
For a large OSS project such as our Qt case study, manual assessment of the over 72,000 comments is a daunting task.
We propose that semantic similarity is a practical, cost-efficient, and empirically assurable approach for assisting with such assessments.
Our case-study results indicate that our approach can classify comments with an average F-measure score of 0.73 and reduce classification effort by about 77\%.

### 2014-08-01 sections/conclusion.tex
reword

More work could be done in the future to relate the amount of useful comments to the software quality, perhaps in a similar way to McIntosh's paper \cite{Mcintosh}.
This could enable a way of assessing the quality of review process in a quantitative way.

>>>>

More work could be done in the future to relate the amount of useful comments to the software quality.
This could enable a way of assessing process quality in a quantitative way.
Future work could also consider different models other than semantic similarity.

### 2014-08-01 sections/introduction.tex
reword

\section{Introduction}
Software code review is an established cost-effective software quality management practice.
Its main intent is to  identify  defects early and encourage quality development practices such as adherence to coding standards and improving code readability.
Nowadays less formal and lightweight code reviews such as Modern Code Review (MCR)\cite{Bacchelli2013a} have received much attention and are commonly used within both industry and OSS projects.
One reason for this is that with MCR, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}, in-person meetings are not required.
Reviewers can find problems in proposed changes and hold discussions on them by adding comments through a code review tool or a mailing list.
Developers then improve the changes in response to these comments and re-submit for review until the changes are approved.  
%Fig. \ref{fig:process} illustrates a typical MCR process.

>>>>

\section{Introduction}
Software code review is an established cost-effective software quality management practice.
Its main intent is to  identify  defects early and encourage quality development practices such as adherence to coding standards and improving code readability.
Nowadays, less formal and lightweight code reviews such as Modern Code Review (MCR)\cite{Bacchelli2013a} have received much attention and are commonly used within both industry and OSS projects.
One reason for this is that with MCR, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}, in-person meetings are not required.
Reviewers can find problems in proposed changes and hold discussions on them by adding comments through a code review tool or a mailing list.
Developers then improve the changes in response to these comments and re-submit for review until the changes are approved.  
%Fig. \ref{fig:process} illustrates a typical MCR process.
